Drivers of sex differences in consumption

### 2017-06-20 ms2/ms2.Rmd
cnst rename
cleaning up

# To do

- filter by HRRs, not states

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, autodep=TRUE)
import::from(broom, tidy)
```

@@

```{r load_abg}
resistance_groups = read_tsv('resistance_groups.tsv')
bug_names = read_tsv('bug_names.tsv')

abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

@@

# Keep only the abundant bug/drug combinations
min_n_states = 35
good_combos = semi_join(abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= min_n_states)

abg %<>% right_join(good_combos, by=c('bug', 'drug_group')) %>%
  rename(bug_long=bug) %>% left_join(bug_names, by='bug_long') %>% select(-bug_long) %>%
  filter(!is.na(percent_nonsusceptible), !is.na(n_isolates))

@@

I started by considering these bug/drug combinations:

@@

Then I filtered to keep only those bug/drug combinations that were present in `r min_n_states` states. That means I'm looking at these `r nrow(good_combos)` bug/drug combinations:

`r good_combos %>% arrange(desc(n_places)) %>% kable`

@@

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  filter(bug %in% c('E. coli', 'Eb. cloacae', 'CNST', 'MSSA', 'MRSA', 'S. pneumoniae')) %>%
  ggplot(aes(x=cpb, y=mean_percent_nonsusceptible, color=drug_group, shape=bug)) +
  geom_point() +
  xlab('claims per beneficiary')
```

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, autodep=TRUE)
import::from(broom, tidy)
import::from(tools, md5sum)
```

@@

```{r load_abg, cache.extra=md5sum('bug_drug.tsv')}
resistance_groups = read_tsv('resistance_groups.tsv')
bug_names = read_tsv('bug_names.tsv')

raw_abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

@@

# Keep only the abundant bug/drug combinations
#min_n_states = 25
#good_combos = semi_join(raw_abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
#  select(bug, drug_group, state) %>%
#  distinct %>%
#  count(bug, drug_group) %>% ungroup() %>% 
#  rename(n_places=n) %>%
#  filter(n_places >= min_n_states)

abg = raw_abg %>%
  #right_join(good_combos, by=c('bug', 'drug_group')) %>%
  right_join(possible_bug_drug, by=c('bug', 'drug_group')) %>%
  rename(bug_long=bug) %>% left_join(bug_names, by='bug_long') %>% select(-bug_long) %>%
  filter(!is.na(percent_nonsusceptible), !is.na(n_isolates))

@@

I started by considering these bug/drug combinations on the basis of their clinical relevance and plausibility:

@@

In previous iterations, I filtered by the number of states in which each bug/drug combination appeared. Increasing that threshold ends up testing the relationships for which we have the best data, and therefore we are the best powered for. Unfortunately, my simulations mostly make it seem like we should, to get the best power, use all the bug/drug combinations.

```{r, eval=FALSE}
#Then I filtered to keep only those bug/drug combinations that were present in `r min_n_states` states. That means I'm looking at these `r nrow(good_combos)` bug/drug combinations:

#`r good_combos %>% arrange(desc(n_places)) %>% kable`
```

@@

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  filter(bug %in% c('E. coli', 'Eb. cloacae', 'CoNS', 'MSSA', 'MRSA', 'S. pneumoniae')) %>%
  ggplot(aes(x=cpb, y=mean_percent_nonsusceptible, color=drug_group, shape=bug)) +
  geom_point() +
  xlab('claims per beneficiary')
```

@@

### Comparing state and HRR

HRR-level Spearman correlations between consumption and resistance (almost) always underestimate the correlation reported at the state level:

```{r}
bind_rows(mutate(results, group='state'),
          mutate(hrr_results, group='hrr')) %>%
  filter(model=='spearman') %>%
  arrange(estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group)) %>%
  select(bug_drug, group, estimate) %>%
  spread(group, estimate) %>%
  ggplot(aes(x=state, y=hrr, label=bug_drug)) +
  geom_point() +
  geom_text() +
  geom_abline()
```

### 2017-06-20 sex-difference/sex-difference.Rmd
cleaning up

sex_icd = read_tsv('sex_codes.tsv', col_types=cols(code='c')) %>%
  rename(dx_code=code, dx_desc=short_desc)

dx = read_tsv(sprintf('../../data/dx_car_claims_%i.tsv', year), col_types=cols(diagnosis='c')) %>%
  select(bene_id=BENE_ID, dx_code=diagnosis) %>%
  left_join(sex_icd, by='dx_code')

dx_counts = dx %>%
  count(dx_code)

bene_dx = dx %>%
  select(bene_id, diagnosis_type) %>%
  distinct() %>%
  mutate(val=TRUE) %>%
  spread(diagnosis_type, val)

@@

bene = read_tsv(sprintf('../bene_%i.tsv', year)) %>%
  mutate(is_female=sex=='female', is_white=race=='white') %>%
  left_join(total_pde, by='bene_id') %>% replace_na(list(n_claims=0)) %>%
  left_join(bene_dx, by='bene_id') %>% replace_na(list(acute_rc=FALSE, copd=FALSE, uti=FALSE))
```

@@

```{r}
sex_icd %>%
  left_join(dx_counts, by='dx_code') %>%
  arrange(diagnosis_type, desc(n)) %>%
  mutate(n=format(n, big.mark=',')) %>%
  kable(align='lllr')
```

>>>>

sex_icd = read_tsv('sex_codes.tsv', col_types=cols(code='c'))

dx_car = sprintf('../../data/dx_car_claims_%i.tsv', year) %>%
  read_tsv(col_types=cols(diagnosis='c'))
dx_op = sprintf('../../data/dx_op_claims_%i.tsv', year) %>%
  read_tsv(col_types=cols(diagnosis='c'))

dx = bind_rows(dx_car, dx_op) %>%
  mutate(date=dmy(from_date)) %>%
  select(bene_id=BENE_ID, date, code=diagnosis) %>%
  left_join(sex_icd, by='code')

dx_counts = dx %>%
  count(code)

bene_dx = dx %>%
  select(bene_id, diagnosis_type) %>%
  distinct() %>%
  mutate(dummy=TRUE) %>%
  spread(diagnosis_type, dummy)

rc_dx = dx %>%
  filter(diagnosis_type=='acute_rc') %>%
  select(bene_id, date) %>%
  group_by(bene_id) %>%
  summarize(n_acute_rc=length(unique(date)))

@@

cc = read_feather(sprintf('../cc_%i.feather', year))

bene = read_tsv(sprintf('../bene_%i.tsv', year)) %>%
  mutate(is_female=sex=='female', is_white=race=='white') %>%
  left_join(total_pde, by='bene_id') %>% replace_na(list(n_claims=0)) %>%
  left_join(bene_dx, by='bene_id') %>% replace_na(list(acute_rc=FALSE, copd=FALSE, uti=FALSE)) %>%
  left_join(select(cc, bene_id, COPD), by='bene_id') %>%
  left_join(rc_dx, by='bene_id') %>% replace_na(list(n_acute_rc=0))
```

@@

```{r}
sex_icd %>%
  left_join(dx_counts, by='code') %>%
  arrange(diagnosis_type, desc(n)) %>%
  mutate(n=format(n, big.mark=',')) %>%
  kable(align='lllr')
```
